[dcpo_demsupport]

### 2020-07-28 paper/dcpo_demsupport.Rmd
use sprintf not round for increase_cy and increase_cyi
clean up

increase_cy <- round((dcpo_input_ncy/supdem_ncy - 1) * 100, 1)
increase_cyi <- round((dcpo_input_ncyi/supdem_ncyi - 1) * 100, 1)
```

@@

save(dcpo_input, dcpo_x_pred, file = here::here("data", "dcpo_y_r_pred.rda"))
```

>>>>

increase_cy <- sprintf("%2.1f", (dcpo_input_ncy/supdem_ncy - 1) * 100, 1)
increase_cyi <- sprintf("%2.1f", (dcpo_input_ncyi/supdem_ncyi - 1) * 100, 1)
```

@@

save(dcpo_input, dcpo_y_r_pred, file = here::here("data", "dcpo_y_r_pred.rda"))
```
